Copy number inference with InferCNV

### 2024-05-22 analyses/cell-type-ewings/template_notebooks/04-infercnv.Rmd

---
title: "Copy number inference with InferCNV"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_genes_classification_file: "../results/annotate_tumor_cells_output/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  infercnv_dir: "../results/annotate_tumor_cells_output/SCPCS000490/infercnv/endothelial_reference"
  results_dir: "../results/annotate_tumor_cells_output/SCPCS000490"
---

@@

# with ref cnv metadata file 
cnv_metadata_file <- file.path(params$infercnv_dir, "endothelial_reference", glue::glue("{params$library_id}_cnv-metadata.tsv"))

# full infercnv object with information on genes/ chr to use later 
final_cnv_obj_file <- file.path(params$infercnv_dir, "endothelial_reference", glue::glue("{params$library_id}_cnv-obj.rds"))

@@

```{r}
# make sure files exist
stopifnot(
  "SCE file is missing" = file.exists(sce_file),
  "PNG file with heatmap is missing" = file.exists(png_file),
  "CNV metadata file is missing" = file.exists(cnv_metadata_file),
  "Final InferCNV object is missing" = file.exists(final_cnv_obj_file),
  "Marker gene classifications are missing" = file.exists(params$marker_genes_classification_file)
)
```

@@

# read in tumor normal classifications 
manual_classifications_df <- readr::read_tsv(params$marker_genes_classification_file)

>>>>

---
title: "Copy number inference with InferCNV"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/annotate_tumor_cells_output/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  infercnv_dir: "../results/annotate_tumor_cells_output/SCPCS000490/infercnv"
  results_dir: "../results/annotate_tumor_cells_output/SCPCS000490"
---

@@

# with ref cnv metadata file 
cnv_metadata_file <- file.path(params$infercnv_dir, glue::glue("{params$library_id}_cnv-metadata.tsv"))

# full infercnv object with information on genes/ chr to use later 
final_cnv_obj_file <- file.path(params$infercnv_dir, glue::glue("{params$library_id}_cnv-obj.rds"))

@@

```{r}
# make sure files exist
stopifnot(
  "SCE file is missing" = file.exists(sce_file),
  "PNG file with heatmap is missing" = file.exists(png_file),
  "CNV metadata file is missing" = file.exists(cnv_metadata_file),
  "Final InferCNV object is missing" = file.exists(final_cnv_obj_file),
  "Marker gene classifications are missing" = file.exists(params$marker_gene_classification)
)
```

@@

# read in tumor normal classifications 
manual_classifications_df <- readr::read_tsv(params$marker_gene_classification)
